\bfseries\LARGE\singlespacing{Spatiotemporal modeling of \emph{Mycobacterium tuberculosis} transmission risks using environmental, clinical, and patient movement data}

### 2023-08-08 doc/paper/manuscript.tex
Updates from Overleaf

Supplementary Table~\zref{tab:data-overview} in \supp provides an overview of the collected data, which is described in the following.

@@

Four devices monitored indoor CO$_2$ levels (Digital CO2 Monitor Carbon Dioxide Meter XE-2000, XEAST, Guangdong, China) in the waiting room, corridor, and TB treatment room (Supplementary Figure 1). CO$_2$ concentrations were recorded in parts per million (ppm) at 1-minute intervals (Supplementary Table 1). Missing values were linearly imputed, except for October~13 where the corridor's CO$_2$ levels were almost completely missing. Here we assumed the same levels as in the waiting room because both rooms had also similar CO$_2$ levels on the other days.

@@

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Flow chart illustrating the spatiotemporal modeling approach from data (blue) to the modeling (yellow).}
    \label{fig:modeling-flow}
\end{figure}

>>>>

@@

Four devices monitored indoor CO$_2$ levels (Digital CO$_2$ Monitor Carbon Dioxide Meter XE-2000, XEAST, Guangdong, China) in the waiting room, corridor, and TB treatment room (Supplementary Figure 1). CO$_2$ concentrations were recorded in parts per million (ppm) at 1-minute intervals (Supplementary Table 1). Missing values were linearly imputed, except for October~13 where the corridor's CO$_2$ levels were almost completely missing. Here we assumed the same levels as in the waiting room because both rooms had also similar CO$_2$ levels on the other days.

@@

\begin{figure}[!htpb]
    \centering
    \includegraphics{doc/paper/flow-chart.pdf}
    \caption{Flow chart of the spatiotemporal modeling approach illustrating the steps from data (blue) to modeling (yellow).}
    \label{fig:modeling-flow}
\end{figure}
